Algorithm explanation

### 2013-09-26 article/horn.tex
Small fixes
Stash
Interpolation
Horn

@@

This construction of the algorithm enables us to compute a relatively
simpler solution compared to existing algorithms while preserving the
computation cost in a reasonable time.

@@

\paragraph {Tree interpolation}
First, consider the following example.

\begin{align*}
x \leq 1 & \implies A(x) \\
y \leq 2 & \implies B(y) \\
A(x) \wedge B(y) & \implies 3x+2y \leq 10
\end{align*}

In this example, we would like to compute linear arithmetic formulas
for the predicate variables $A$ and $B$.  They appear only once on
both left-hand and right-hand globally in the problem.

We try to obtain a simple solution that is expressed by linear
expression templates, whose coefficients and constants are
parameterized.  Assume that they have following predicate templates.

\begin{align*}
A(x) : c_1 x + c_2 \leq 0 \\
B(y) : c_3 y + c_4 \leq 0
\end{align*}

By naturally encoding the first Horn clause with Farkas's lemma, we
obtain a linear constraint
$\lambda_1 = c_1 \wedge - \lambda_1 \geq c_2 \wedge \lambda_1 \geq 0$.
Any assignment to $ c_1, c_2, \lambda_1 $ which satisfies this will
make $A(x)$ valid for the first clause.  In the same manner, we obtain
$\lambda_2 = c_3 \wedge - 2 \lambda_2 \geq c_4 \wedge \lambda_2 \geq 0$
from the second clause, and 
$c_1 = 3 \lambda_3 \wedge c_3 = 2 \lambda_3 \wedge c_2 + c_4 \geq -10 \lambda_3 \wedge \lambda_3 > 0$
from the third.

One of the models satisfying all the constraints above is
$( c_1, c_2, c_3, c_4, \lambda_1, \lambda_2, \lambda_3 ) = (3, -3, 2, -4, 3, 2, 1)$.
By assigning them to the template, we obtain the following solution.

\begin{align*}
A(x) : 3 x - 3 \leq 0 \\
B(y) : 2 y - 4 \leq 0
\end{align*}

\paragraph {DAG problem solving}
Second, we explain a case that some predicate variables appear
multiple times on left-hand side in different Horn clauses.

\begin{align*}
x \leq 1 & \implies A(x) \\
A(x) \wedge A(y) & \implies x+y \leq 2
\end{align*}

Assigning a template $A(x) : c_1 x + c_2 \leq 0$, we obtain the same
constraint for the first clause as the previous example.

\begin{align} \label{eq:constr1}
\lambda_1 = c_1 \wedge - \lambda_1 \geq c_2 \wedge \lambda_1 \geq 0
\end{align}

Since we have $A$'s appearance twice on the second clause, it is
possible for $A$ to have two expressions each of which is used for
$A(x)$ and $A(y)$.  Although we need to use the same template for
multiple occurrences in order to compute the simplest solution, it may
make the whole constraints unsatisfiable if the simplest solution does
not exist.

Therefore, we generate a weaker constraint for the second clause that
allows different expressions of $A$ for multiple occurrence.  If the
whole constraint is satisfiable in the case, we try to solve in a
stronger constraint to generate a simple solution.

In this specific case, it is virtually equivalent to solve the
following problem in a weaker constraint.

\begin{align*}
\text{Problem:} \\
x \leq 1 & \implies A_1(x) \\
x \leq 1 & \implies A_2(x) \\
A_1(x) \wedge A_2(y) & \implies x+y \leq 2 \\
\\
\text{Templates:} \\
A_1(x) \text{ : } & c_{1,1} x + c_{2,1} \leq 0 \\
A_2(x) \text{ : } & c_{1,2} x + c_{2,2} \leq 0 \\
A(x) \text{ : } & A_1(x) \wedge A_2(x) \\
\end{align*}

By duplicating the constraint~\ref{eq:constr1} of $A$ for newly
created $A_1$ and $A_2$, we obtain the whole constraint as follows.

\begin{align*}
& \lambda_{1,1} = c_{1,1} \wedge - \lambda_{1,1} \geq c_{2,1} \wedge \lambda_{1,1} \geq 0 \wedge \\
& \lambda_{1,2} = c_{1,2} \wedge - \lambda_{1,2} \geq c_{2,2} \wedge \lambda_{1,2} \geq 0 \wedge \\
& c_{1,1} = \lambda_2 \wedge c_{1,2} = \lambda_2 \wedge c_{2,1} + c_{2,2} \geq 2 \lambda_2 \wedge \lambda_2 > 0
\end{align*}

@@

\paragraph {Disjunctive Horn clause solving}
Finally, we explain a case that an input set of Horn clauses contain
disjunctions on left-hand side.

\begin{align*}
x \leq 0 \wedge -x \leq 0 & \implies A(x) \\
x+1 \leq 0 \vee -x+1 \leq 0 & \implies B(x) \\
A(x) \wedge B(x) & \implies 1 \leq 0
\end{align*}

Same as the previous examples, templates for predicate variables are
prepared.

\begin{align*}
A(x) : c_1 x + c_2 \leq 0 \\ B(x) : c_3 x + c_4 \leq 0
\end{align*}

The constraints generated are follows.

\begin{align*}
& \lambda_1 - \lambda_2 = c_1 \wedge 0 \geq c_2 \wedge \lambda_1 \geq 0 \wedge \lambda_2 \geq 0 \wedge \\
& \lambda_3 = c_3 \wedge \lambda_3 \geq c_4 \wedge \lambda_3 \geq 0 \wedge \\
& - \lambda_4 = c_3 \wedge \lambda_4 \geq c_4 \wedge \lambda_4 \geq 0 \wedge \\
& c_1 + c_3 = 0 \wedge c_2 + c_4 > 0
\end{align*}

The constraints here become unsatisfiable, and one possible
unsatisfiable core is:

\begin{align*}
\lambda_3 & = c_3 \\
\lambda_3 & \geq c_4 \\
- \lambda_4 & = c_3 \\
\lambda_4 & \geq c_4 \\
c_2 + c_4 & > 0 \\
0 & \geq c_2
\end{align*}

@@

Now we slightly change the problem and the template.

\begin{align*}
\text{Problem:} \\
x \leq 0 \wedge -x \leq 0 & \implies A(x) \\
x+1 \leq 0 & \implies B_1(x) \\
-x+1 \leq 0 & \implies B_2(x) \\
A(x) \wedge B_1(x) & \implies 1 \leq 0 \\
A(x) \wedge B_2(x) & \implies 1 \leq 0 \\
\\
\text{Templates:} \\
A(x) \text{ : } & c_1 x + c_2 \leq 0 \\
B_i(x) \text{ : } & c_{3,i} x + c_{4,i} \leq 0 \quad (i \in \left\lbrace 1,2 \right\rbrace ) \\
B(x) \text{ : } & B_1(x) \vee B_2(x)
\end{align*}

When we construct the constraints, as same as previous, we again
obtain an unsatisfiable core:

\begin{align*}
\text{Constraint:} \\
& \lambda_1 - \lambda_2 = c_1 \wedge 0 \geq c_2 \wedge \lambda_1 \geq 0 \wedge \lambda_2 \geq 0 \wedge \\
& \lambda_3 = c_{3,1} \wedge \lambda_3 \geq c_{4,1} \wedge \lambda_3 \geq 0 \wedge \\
& \lambda_3 = c_{3,2} \wedge \lambda_3 \geq c_{4,2} \wedge \lambda_3 \geq 0 \wedge \\
& - \lambda_4 = c_{3,1} \wedge \lambda_4 \geq c_4 \wedge \lambda_4 \geq 0 \wedge \\
& - \lambda_4 = c_{3,2} \wedge \lambda_4 \geq c_{4,2} \wedge \lambda_4 \geq 0 \wedge \\
& c_1 + c_{3,1} = 0 \wedge c_2 + c_{4,1} > 0 \wedge \\
& c_1 + c_{3,2} = 0 \wedge c_2 + c_{4,2} > 0
\\
\text{Unsatisfiable core:} \\
0 \geq c_2 \\
& \lambda_3 = c_{3,1} \wedge \lambda_3 \geq c_{4,1} \wedge \\
& - \lambda_4 = c_{3,2} \wedge \\
& c_1 + c_{3,1} = 0 \wedge c_2 + c_{4,1} > 0 \wedge \\
& c_1 + c_{3,2} = 0
\end{align*}

This time, the unsatisfiable core contains the constraints that
originate from

\begin{align*}
\text{Problem:} \\
x \leq 0 \wedge -x \leq 0 & \implies A_i(x) \quad (i \in \left\lbrace 1,2 \right\rbrace ) \\
x+1 \leq 0 & \implies B_1(x) \\
-x+1 \leq 0 & \implies B_2(x) \\
A_i(x) \wedge B_j(x) & \implies 1 \leq 0 \quad (i,j \in \left\lbrace 1,2 \right\rbrace ) \\
\\
\text{Templates:} \\
A_i(x) \text{ : } & c_{1,i} x + c_{2,i} \leq 0 \quad (i \in \left\lbrace 1,2 \right\rbrace ) \\
A(x) \text{ : } & A_1(x) \wedge A_2(x) \\
B_i(x) \text{ : } & c_{3,i} x + c_{4,i} \leq 0 \quad (i \in \left\lbrace 1,2 \right\rbrace ) \\
B(x) \text{ : } & B_1(x) \vee B_2(x)
\end{align*}

After this, we obtain the following constraint:

\begin{align*}
& \lambda_1 - \lambda_2 = c_{1,1} \wedge 0 \geq c_{2,1} \wedge \lambda_1 \geq 0 \wedge \lambda_2 \geq 0 \wedge \\
& \lambda_1 - \lambda_2 = c_{1,2} \wedge 0 \geq c_{2,2} \wedge \lambda_1 \geq 0 \wedge \lambda_2 \geq 0 \wedge \\
& \lambda_3 = c_{3,1} \wedge \lambda_3 \geq c_{4,1} \wedge \lambda_3 \geq 0 \wedge \\
& \lambda_3 = c_{3,2} \wedge \lambda_3 \geq c_{4,2} \wedge \lambda_3 \geq 0 \wedge \\
& - \lambda_4 = c_{3,1} \wedge \lambda_4 \geq c_4 \wedge \lambda_4 \geq 0 \wedge \\
& - \lambda_4 = c_{3,2} \wedge \lambda_4 \geq c_{4,2} \wedge \lambda_4 \geq 0 \wedge \\
& c_{1,1} + c_{1,2} + c_{3,1} = 0 \wedge c_{2,1} + c_{2,2} + c_{4,1} > 0 \wedge \\
& c_{1,1} + c_{1,2} + c_{3,2} = 0 \wedge c_{2,1} + c_{2,2} + c_{4,2} > 0
\end{align*}

By continuing this process, the process in the end generates a
predicate template that the solution will become.  Eventually, we
obtain the following solution.

\begin{align*}
A(x) \text{ : } & x \leq 0 \wedge -x \leq 0 \\
B(x) \text{ : } & x+1 \leq 0 \vee -x+1 \leq 0
\end{align*}

@@

\paragraph{Conjunction split}
For the first case previously mentioned, the unsatisfiable core
$\mathcal{U}$ contains coefficient constraint expressions with a
coefficient parameter of certain predicate variable.  If the predicate
variable $P$ is the cause of unsatisfiability, some constraint
expressions in the unsatisfiable core have a parameter $a_{P,i}$
and/or $b_P$ in the following way.
\begin{align*}
% TODO:
& \exists v_a, v_b \in V_T; v_P \leadsto v_a \wedge v_P \leadsto v_b \wedge \\
& \left( \exists i, j, k;
\left\lbrace \left( \mathbf{a}_{v_a,j} = \ldots + \mathbf{a}_{v_P,i} + \ldots \right),
\left( \mathbf{a}_{v_b,k} = \ldots + \mathbf{a}_{v_P,i} + \ldots \right)
\right\rbrace \subseteq \mathcal{U} \right)
\end{align*}

@@

<fig...>

@@

\paragraph{Disjunction split}
For the second case, the unsatisfiable core $\mathcal{U}$ contains
coefficient constraints that unifies induced linear expressions from
each term in disjunctions to be the same expression.  Similarly as
previous, if the predicate variable $P$ is the cause of
unsatisfiability, some constraint expressions in the unsatisfiable
core have a parameter $a_{P,i}$ and/or $b_P$ in the following way.
\begin{align*}
% TODO:
& \exists v_a, v_b \in V_T; v_P \leadsto v_a \wedge v_P \leadsto v_b \wedge \\
& \left( \exists i, j, k;
\left\lbrace \left( \mathbf{a}_{v_a,j} = \ldots + \mathbf{a}_{v_P,i} + \ldots \right),
\left( \mathbf{a}_{v_b,k} = \ldots + \mathbf{a}_{v_P,i} + \ldots \right)
\right\rbrace \subseteq \mathcal{U} \right)
\end{align*}

@@

<fig...>

@@

Consider these two ways of transformation, we show a pseudo-code for
\linebreak \transGraph~procedure.  The procedure is given the graph
$G$, the predicate templateset $T$, and the unsatisfiable core
$\mathcal{U}$. It returns the transformed graph $G'$ and the new
templateset $T'$.

\begin{algorithm}
\caption{$ \transGraph (G, T, \mathcal{U}) $}\label{alg:transGraph}
\begin{algorithmic}
% TODO:
\RETURN {$\left( G', T' \right)$}
\end{algorithmic}
\end{algorithm}

@@

Consider example below. $e_i$ represents some conjunctions of linear
expressions.
% TODO: Can't we replace e_i with actual expressions?
\begin{align*}
(e_1 \vee e_2) \implies P \\ (e_3 \vee e_4) \implies Q \\ P \wedge Q \implies \bot
\end{align*}
In this example, a na\"{i}ve algorithm may solve following four
problems separately.
\begin{itemize}
\item $e_1 \implies P_1 \qquad e_3 \implies Q_1 \qquad P_1 \wedge Q_1 \implies \bot$
\item $e_2 \implies P_2 \qquad e_3 \implies Q_2 \qquad P_2 \wedge Q_2 \implies \bot$
\item $e_1 \implies P_3 \qquad e_4 \implies Q_3 \qquad P_3 \wedge Q_3 \implies \bot$
\item $e_2 \implies P_4 \qquad e_4 \implies Q_4 \qquad P_4 \wedge Q_4 \implies \bot$
\end{itemize}
Then the solution is built by follows.
\begin{itemize}
\item $P = ( P_1 \vee P_2 ) \wedge ( P_3 \vee P_4 )$
\item $Q = ( P_1 \vee P_3 ) \wedge ( P_2 \vee P_4 )$
\end{itemize}
However, this method is not efficient.

@@

Note that duplicating the constraint in a na\"{i}ve way may cause the
constraint to exponentially grow in size.  Our algorithm prevent it by
simplifying a predicate vertex's constraint $C_v$ by quantifier
elimination when $v$ is duplicated in generating linear constraint.
For a predicate variable vertex $v_P$, variables except for the
coefficient parameter $\mathbf{a}_P$ and the constant parameter $b_P$
are eliminated.  Due to the constraints generation process, the
simplified constraint is also linear and can be efficiently check the
satisfiability.

@@

\begin{algorithm}
\caption{$ \genConstr (G, v, V_\star) $}\label{alg:genConstr}
\begin{algorithmic}
\STATE {$C \gets \emptyset$}
\FORALL {$v_\Rightarrow \in preds_G(v)$}
  \FORALL {$v_p \in preds_G(v_\Rightarrow)$}
    \IF {$\varphi (v_p)$ is a predicate variable}
      \STATE {$C \gets C \cup \genConstr (G, v_p, visited)$}
    \ELSE
      \STATE { $id$ }
    \ENDIF
  \ENDFOR
\ENDFOR
\end{algorithmic}
\end{algorithm}

>>>>

The problems are generated by encoding constraints over execution
paths with unknown predicates which describe functions' constraints
between parameters and return values.

@@

This construction of the algorithm enables us to compute a relatively
simpler solution compared to existing algorithms while restraining the
computation cost in a reasonable time.

@@

\begin{figure}\label{fig:ex1}
\begin{center}
\includegraphics[scale=0.8]{figures/ex1.eps}
\end{center}
\vspace{-18pt}
\caption{Problem visualization for tree interpolation example}
\end{figure}

\paragraph {Tree interpolation}
First, consider the following example.
\begin{align*}
x \leq 1 & \implies A(x) \\
y \leq 2 & \implies B(y) \\
A(x) \wedge B(y) & \implies 3x+2y \leq 10
\end{align*}
In this example, we would like to compute linear arithmetic formulas
for the predicate variables $A$ and $B$.  They appear only once on
both left-hand and right-hand globally in the problem.  For ease of
understanding, we visualized the problem by a graph in Figure~\ref{fig:ex1}.

We try to obtain a simple solution that is expressed by linear
expression templates, whose coefficients and constants are
parameterized.  Assume that they have following predicate templates.
\begin{align*}
A(x) : c_1 x + c_2 \leq 0 \\
B(y) : c_3 y + c_4 \leq 0
\end{align*}

By naturally encoding the first Horn clause with Farkas's lemma, we
obtain a linear constraint
$(\lambda_1 = c_1) \wedge (- \lambda_1 \geq c_2) \wedge (\lambda_1 \geq 0)$.
Any assignment to $ c_1, c_2, \lambda_1 $ which satisfies this will
make $A(x)$ valid for the first clause.  In the same manner, we obtain
$(\lambda_2 = c_3) \wedge (- 2 \lambda_2 \geq c_4) \wedge (\lambda_2 \geq 0)$
from the second clause, and 
$(c_1 = 3 \lambda_3) \wedge (c_3 = 2 \lambda_3) \wedge (c_2 + c_4 \geq -10 \lambda_3) \wedge (\lambda_3 > 0)$
from the third.

One of the models satisfying all the constraints above is
\[( c_1, c_2, c_3, c_4, \lambda_1, \lambda_2, \lambda_3 ) = (3, -3, 2, -4, 3, 2, 1) \].
By assigning them to the template, we obtain the following solution.
\begin{align*}
A(x) : 3 x - 3 \leq 0 \\
B(y) : 2 y - 4 \leq 0
\end{align*}

\paragraph {DAG problem solving}

\begin{figure}\label{fig:ex21}
\begin{center}
\includegraphics[scale=0.8]{figures/ex2-1.eps}
\end{center}
\caption{Problem visualization for DAG structured example}
\end{figure}

Second, we explain a case that some predicate variables appear
multiple times on left-hand side in different Horn clauses.
\begin{align*}
x \leq 1 & \implies A(x) \\
A(x) \wedge A(y) & \implies x+y \leq 2
\end{align*}
Problem visualization is available in Figure~\ref{fig:ex21}. Note
that the graph now takes a DAG structure.

Assigning a template $A(x) : c_1 x + c_2 \leq 0$, we obtain the same
constraint for the first clause as the previous example.
\begin{align*} \label{eq:constr1}
(\lambda_1 = c_1) \wedge (- \lambda_1 \geq c_2) \wedge (\lambda_1 \geq 0)
\end{align*}

Since we have $A$'s appearance twice on the second clause, it is
possible for $A$ to have two expressions each of which is used for
$A(x)$ and $A(y)$.  Although we need to use the same template for
multiple occurrences in order to compute the simplest solution, it may
generally make the whole constraints unsatisfiable if the simplest
solution does not exist.

The above case eventually generate the constraint
\begin{align*}
& (\lambda_1 = c_1) \wedge (- \lambda_1 \geq c_2) \wedge (\lambda_1 \geq 0) \wedge \\
& (c_1 = \lambda_2) \wedge (2 c_2 \geq 2 \lambda_2) \wedge (\lambda_2 > 0)
\end{align*}
and we may get a model $(c_1, c_2, \lambda_1) = (1, -1, 1)$ to
obtain $Ax - 1 \leq 0$ for $A(x)$.

\begin{figure}[htb]
  \begin{minipage}[t]{.47\textwidth}
  \centering
  \includegraphics[scale=0.8]{figures/ex2-2.eps}
  \label{fig:ex22}
  \caption{Interpolation}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{.47\textwidth}
  \centering
  \includegraphics[scale=0.8]{figures/ex2-3.eps}
  \label{fig:ex23}
  \caption{Interpolation}
  \end{minipage}
\end{figure}

Now we slightly change the problem.
\begin{align*}
x \leq 1 & \implies A(x) \\
A(x) \wedge A(y) & \implies x+2y \leq 3
\end{align*}
It is visualized in Figure~\ref{fig:ex22}.  The modifed constraint is
\begin{align*}
& (\lambda_1 = c_1) \wedge (- \lambda_1 \geq c_2) \wedge (\lambda_1 \geq 0) \wedge \\
& (c_1 = \lambda_2) \wedge (c_1 = 2\lambda_2) \wedge (2 c_2 \geq 3 \lambda_2) \wedge (\lambda_2 > 0)
\end{align*}
No solution exists for this constraint.  Therefore we generate a
weaker constraint for the second clause that allows different
expressions of $A$ for multiple occurrence.  If the whole constraint
is satisfiable in the case, we try to solve in a stronger constraint
to generate a simple solution.

In this specific case, it is virtually equivalent to solve the
following problem in a weaker constraint.
\begin{align*}
\text{Problem:} \\
x \leq 1 & \implies A_1(x) \\
x \leq 1 & \implies A_2(x) \\
A_1(x) \wedge A_2(y) & \implies x+y \leq 2 \\
\\
\text{Templates:} \\
A_1(x) \text{ : } & c_{1,1} x + c_{2,1} \leq 0 \\
A_2(x) \text{ : } & c_{1,2} x + c_{2,2} \leq 0 \\
A(x) \text{ : } & A_1(x) \wedge A_2(x) \\
\end{align*}
Figure~\ref{fig:ex23} illustrates above.  By duplicating the
constraint~\ref{eq:constr1} of $A$ for newly created $A_1$ and $A_2$,
we obtain the whole constraint as follows.
\begin{align*}
& \lambda_{1,1} = c_{1,1} \wedge - \lambda_{1,1} \geq c_{2,1} \wedge \lambda_{1,1} \geq 0 \wedge \\
& \lambda_{1,2} = c_{1,2} \wedge - \lambda_{1,2} \geq c_{2,2} \wedge \lambda_{1,2} \geq 0 \wedge \\
& c_{1,1} = \lambda_2 \wedge c_{1,2} = \lambda_2 \wedge c_{2,1} + c_{2,2} \geq 2 \lambda_2 \wedge \lambda_2 > 0
\end{align*}

@@

\paragraph {Disjunctive Horn clause solving}
Finally, we explain a case that an input set of Horn clauses contain
disjunctions on left-hand side.
\begin{figure}\label{fig:ex31}
  \begin{center}
    \includegraphics[scale=0.8]{figures/ex3-1.eps}
  \end{center}
  \caption{Visualization of disjunctive Horn clause problem}
\end{figure}
\begin{align*}
x \leq 0 \wedge -x \leq 0 & \implies A(x) \\
x+1 \leq 0 \vee -x+1 \leq 0 & \implies B(x) \\
A(x) \wedge B(x) & \implies 1 \leq 0
\end{align*}
See Figure~\ref{fig:ex31}.  Same as the previous examples, templates
for predicate variables are prepared.
\begin{align*}
A(x) : c_1 x + c_2 \leq 0 \\ B(x) : c_3 x + c_4 \leq 0
\end{align*}
The constraints generated are follows.
\begin{align*}
& \lambda_1 - \lambda_2 = c_1 \wedge 0 \geq c_2 \wedge \lambda_1 \geq 0 \wedge \lambda_2 \geq 0 \wedge \\
& \lambda_3 = c_3 \wedge \lambda_3 \geq c_4 \wedge \lambda_3 \geq 0 \wedge \\
& - \lambda_4 = c_3 \wedge \lambda_4 \geq c_4 \wedge \lambda_4 \geq 0 \wedge \\
& c_1 + c_3 = 0 \wedge c_2 + c_4 > 0
\end{align*}
The constraints here become unsatisfiable, and one possible
unsatisfiable core is:
\begin{align*}
\lambda_3 & = c_3 \\
\lambda_3 & \geq c_4 \\
- \lambda_4 & = c_3 \\
\lambda_4 & \geq c_4 \\
c_2 + c_4 & > 0 \\
0 & \geq c_2
\end{align*}

@@

Now we slightly change the problem and the template as in Figure~\ref{fig:ex32}.
\begin{align*}
\text{Problem:} \\
x \leq 0 \wedge -x \leq 0 & \implies A(x) \\
x+1 \leq 0 & \implies B_1(x) \\
-x+1 \leq 0 & \implies B_2(x) \\
A(x) \wedge B_1(x) & \implies 1 \leq 0 \\
A(x) \wedge B_2(x) & \implies 1 \leq 0 \\
\\
\text{Templates:} \\
A(x) \text{ : } & c_1 x + c_2 \leq 0 \\
B_i(x) \text{ : } & c_{3,i} x + c_{4,i} \leq 0 \quad (i \in \left\lbrace 1,2 \right\rbrace ) \\
B(x) \text{ : } & B_1(x) \vee B_2(x)
\end{align*}

\begin{figure}\label{fig:ex32}
  \begin{center}
    \includegraphics[scale=0.8]{figures/ex3-2.eps}
  \end{center}
  \caption{Example}
\end{figure}
When we construct the constraints, as same as previous, we again
obtain an unsatisfiable core:
\begin{align*}
\text{Constraint:} \\
& \lambda_1 - \lambda_2 = c_1 \wedge 0 \geq c_2 \wedge \lambda_1 \geq 0 \wedge \lambda_2 \geq 0 \wedge \\
& \lambda_3 = c_{3,1} \wedge \lambda_3 \geq c_{4,1} \wedge \lambda_3 \geq 0 \wedge \\
& \lambda_3 = c_{3,2} \wedge \lambda_3 \geq c_{4,2} \wedge \lambda_3 \geq 0 \wedge \\
& - \lambda_4 = c_{3,1} \wedge \lambda_4 \geq c_4 \wedge \lambda_4 \geq 0 \wedge \\
& - \lambda_4 = c_{3,2} \wedge \lambda_4 \geq c_{4,2} \wedge \lambda_4 \geq 0 \wedge \\
& c_1 + c_{3,1} = 0 \wedge c_2 + c_{4,1} > 0 \wedge \\
& c_1 + c_{3,2} = 0 \wedge c_2 + c_{4,2} > 0
\\
\text{Unsatisfiable core:} \\
& 0 \geq c_2 \\
& \lambda_3 = c_{3,1} \\
& \lambda_3 \geq c_{4,1} \\
& - \lambda_4 = c_{3,2} \\
& c_1 + c_{3,1} = 0 \\ & c_2 + c_{4,1} > 0 \\
& c_1 + c_{3,2} = 0
\end{align*}
This time, the unsatisfiable core contains the constraints that
originate from conjunction.  We need to modify the problem again.
\begin{align*}
\text{Problem:} \\
x \leq 0 \wedge -x \leq 0 & \implies A_i(x) \quad (i \in \left\lbrace 1,2 \right\rbrace ) \\
x+1 \leq 0 & \implies B_1(x) \\
-x+1 \leq 0 & \implies B_2(x) \\
A_i(x) \wedge B_j(x) & \implies 1 \leq 0 \quad (i,j \in \left\lbrace 1,2 \right\rbrace ) \\
\\
\text{Templates:} \\
A_i(x) \text{ : } & c_{1,i} x + c_{2,i} \leq 0 \quad (i \in \left\lbrace 1,2 \right\rbrace ) \\
A(x) \text{ : } & A_1(x) \wedge A_2(x) \\
B_i(x) \text{ : } & c_{3,i} x + c_{4,i} \leq 0 \quad (i \in \left\lbrace 1,2 \right\rbrace ) \\
B(x) \text{ : } & B_1(x) \vee B_2(x)
\end{align*}
See Figure~\ref{fig:ex33}.

\begin{figure}\label{fig:ex33}
  \begin{center}
    \includegraphics[scale=0.8]{figures/ex3-3.eps}
  \end{center}
  \caption{Example}
\end{figure}

After this, we obtain the following constraint:
\begin{align*}
& \lambda_1 - \lambda_2 = c_{1,1} \wedge 0 \geq c_{2,1} \wedge \lambda_1 \geq 0 \wedge \lambda_2 \geq 0 \wedge \\
& \lambda_1 - \lambda_2 = c_{1,2} \wedge 0 \geq c_{2,2} \wedge \lambda_1 \geq 0 \wedge \lambda_2 \geq 0 \wedge \\
& \lambda_3 = c_{3,1} \wedge \lambda_3 \geq c_{4,1} \wedge \lambda_3 \geq 0 \wedge \\
& \lambda_3 = c_{3,2} \wedge \lambda_3 \geq c_{4,2} \wedge \lambda_3 \geq 0 \wedge \\
& - \lambda_4 = c_{3,1} \wedge \lambda_4 \geq c_4 \wedge \lambda_4 \geq 0 \wedge \\
& - \lambda_4 = c_{3,2} \wedge \lambda_4 \geq c_{4,2} \wedge \lambda_4 \geq 0 \wedge \\
& c_{1,1} + c_{1,2} + c_{3,1} = 0 \wedge c_{2,1} + c_{2,2} + c_{4,1} > 0 \wedge \\
& c_{1,1} + c_{1,2} + c_{3,2} = 0 \wedge c_{2,1} + c_{2,2} + c_{4,2} > 0
\end{align*}
By solving this, we eventually obtain the following solution.
\begin{align*}
A(x) \text{ : } & x \leq 0 \wedge -x \leq 0 \\
B(x) \text{ : } & x+1 \leq 0 \vee -x+1 \leq 0
\end{align*}

@@

\paragraph{Conjunction split}
For the first case previously mentioned, the unsatisfiable core
$\mathcal{U}$ contains coefficient constraint expressions with a
coefficient parameter of certain predicate variable.  If the predicate
variable $P$ is the cause of unsatisfiability, some constraint
expressions in the unsatisfiable core have a parameter $a_{P,i}$
and/or $b_P$ in the following way.
\begin{align*}
& \exists v_a, v_b \in V_T; v_P \leadsto v_a \wedge v_P \leadsto v_b \wedge \\
& \left( \exists i, j, k;
\left\lbrace \left( \mathbf{a}_{v_a,j} = \ldots + \mathbf{a}_{v_P,i} + \ldots \right),
\left( \mathbf{a}_{v_b,k} = \ldots + \mathbf{a}_{v_P,i} + \ldots \right)
\right\rbrace \subseteq \mathcal{U} \right)
\end{align*}

@@

\vspace{48pt}
\begin{figure}[htb]\label{fig:conj1}
  \begin{minipage}[t]{.47\textwidth}
  \centering
  \includegraphics[scale=0.8]{figures/conj1.eps}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{.47\textwidth}
  \centering
  \includegraphics[scale=0.8]{figures/conj2.eps}
  \end{minipage}
  \caption{Conjunctive split}
\end{figure}

@@

\paragraph{Disjunction split}
For the second case, the unsatisfiable core $\mathcal{U}$ contains
coefficient constraints that unifies induced linear expressions from
each term in disjunctions to be the same expression.  Similarly as
previous, if the predicate variable $P$ is the cause of
unsatisfiability, some constraint expressions in the unsatisfiable
core have a parameter $a_{P,i}$ and/or $b_P$ in the following way.
\begin{align*}
& \exists v_a, v_b \in V_T; v_P \leadsto v_a \wedge v_P \leadsto v_b \wedge \\
& \left( \exists i, j, k;
\left\lbrace \left( \mathbf{a}_{v_a,j} = \ldots + \mathbf{a}_{v_P,i} + \ldots \right),
\left( \mathbf{a}_{v_b,k} = \ldots + \mathbf{a}_{v_P,i} + \ldots \right)
\right\rbrace \subseteq \mathcal{U} \right)
\end{align*}

@@

\vspace{48pt}
\begin{figure}[htb]\label{fig:disj1}
  \begin{minipage}[t]{.47\textwidth}
  \centering
  \includegraphics[scale=0.8]{figures/disj1.eps}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{.47\textwidth}
  \centering
  \includegraphics[scale=0.8]{figures/disj2.eps}
  \end{minipage}
  \caption{Disjunctive split}
\end{figure}

@@

%Consider these two ways of transformation, we show a pseudo-code for
%\linebreak \transGraph~procedure.  The procedure is given the graph
%$G$, the predicate templateset $T$, and the unsatisfiable core
%$\mathcal{U}$. It returns the transformed graph $G'$ and the new
%templateset $T'$.

%\begin{algorithm}
%\caption{$ \transGraph (G, T, \mathcal{U}) $}\label{alg:transGraph}
%\begin{algorithmic}
% TODO:
%\RETURN {$\left( G', T' \right)$}
%\end{algorithmic}
%\end{algorithm}

@@

Consider example below. $e_i$ represents some conjunctions of linear
expressions.
\begin{align*}
(e_1 \vee e_2) \implies P \\ (e_3 \vee e_4) \implies Q \\ P \wedge Q \implies \bot
\end{align*}
In this example, a na\"{i}ve algorithm may solve following four
problems separately.
\vspace*{-8pt}\begin{itemize}\itemsep-3pt
\item $e_1 \implies P_1 \qquad e_3 \implies Q_1 \qquad P_1 \wedge Q_1 \implies \bot$
\item $e_2 \implies P_2 \qquad e_3 \implies Q_2 \qquad P_2 \wedge Q_2 \implies \bot$
\item $e_1 \implies P_3 \qquad e_4 \implies Q_3 \qquad P_3 \wedge Q_3 \implies \bot$
\item $e_2 \implies P_4 \qquad e_4 \implies Q_4 \qquad P_4 \wedge Q_4 \implies \bot$
\end{itemize}
Then the solution is built by follows.
\vspace*{-4pt}\begin{itemize}\itemsep-3pt
\item $P = ( P_1 \vee P_2 ) \wedge ( P_3 \vee P_4 )$
\item $Q = ( P_1 \vee P_3 ) \wedge ( P_2 \vee P_4 )$
\end{itemize}
However, it is obvious that this method is not efficient.

@@

Note that duplicating the constraint in a na\"{i}ve way may cause the
constraint to exponentially grow in size.  Our algorithm prevent it by
simplifying a predicate vertex's constraint $C_v$ by quantifier
elimination when $v$ is duplicated in generating linear constraint.
For a predicate variable vertex $v_P$, variables except for the
coefficient parameter $\mathbf{a}_P$ and the constant parameter $b_P$
are eliminated.  Because the constraints are conjunctive, the
qunatifier elimination is reduced to the problem of polyhedron
projection.

@@

\begin{algorithm}
\caption{$ \genConstr (G, v, V_\star) $}\label{alg:genConstr}
\begin{algorithmic}
\STATE {$C \gets \emptyset$}
\FORALL {$v_\Rightarrow \in preds_G(v)$}
  \FORALL {$v_p \in preds_G(v_\Rightarrow)$}
    \IF {$\varphi (v_p)$ is a predicate variable}
      \STATE {$C' \gets \genConstr (G, v_p, V_\star)$}
      \IF {$v_p \in V_\star$}
        \STATE {$C' \gets \textsc{Simplify}(C')$}
      \ENDIF
      \STATE {$C \gets C \cup C'$}
    \ELSE
      \STATE {$C \gets C \cup \genConstr (G, v_p, V_\star)$}
    \ENDIF
  \ENDFOR
\ENDFOR
\RETURN {$C$}
\end{algorithmic}
\end{algorithm}
